\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge \scshape Andres Cruz} \\ \vspace{2pt}
    \small (786) 262-0053 $|$ \href{mailto:acruz24100@gmail.com}{\underline{acruz24100@gmail.com}} $|$ \href{https://linkedin.com/in/andrescruz}{\underline{linkedin.com/in/andres-cruz}} $|$ \href{https://github.com/andrescruz}{\underline{github.com/andrescruz}} \\ \vspace{5pt}
    \textbf{Availability:} June -- December 2026 (Open to all shifts) $|$ \textbf{Transportation:} Reliable Personal Transportation Available
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{Boston, MA}
      {B.S. Computer Science (AI Concentration), Minor in Mathematics}{Sep 2024 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Object-Oriented Design, Embedded Systems, Calculus III, Algorithms, Physics for Engineering (I \& II), Programming in C++, Computer Systems, Artificial Intelligence, Professional Development}
        \resumeItem{\textbf{Honors:} GPA: 3.84/4.0 $|$ Dean's List}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical \& Engineering Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C++, Python, Java, SQL, TypeScript, C (Embedded)} \\
     \textbf{Engineering \& Hardware}{: Automotive Diagnostics \& Repair, Circuit Analysis, IoT (MQTT/ESP32), 3D Printing, Soldering.} \\
     \textbf{Software Tools}{: Microsoft Office Suite, Linux, Git, VS Code, SolidWorks, AutoCAD, Fusion 360.} \\
     \textbf{Languages}{: English (Native), Spanish (Native/Fluent)}
    }}
 \end{itemize}


%-----------PROJECTS & EXPERIENCE-----------
\section{Engineering Projects \& Experience}
  \resumeSubHeadingListStart

    % Project 1: The "Ride Control" / IoT Project
    \resumeProjectHeading
      {\textbf{Autonomous IoT Access Control System} $|$ \emph{C++, Python, Raspberry Pi, MQTT}}{Miami, FL}
      \resumeItemListStart
        \resumeItem{Engineered a distributed facility access system using \textbf{Python} and \textbf{MQTT} protocols to manage electromechanical locks via facial recognition, mimicking safety-critical logic used in ride access systems.}
        \resumeItem{Programmed fail-safe protocols in \textbf{C++} to ensure the system defaults to a secure state during power interruptions or network failures, prioritizing user safety.}
        \resumeItem{Integrated hardware components (solenoids, relays, camera modules) with software logic to reduce entry friction by 40\%, demonstrating a focus on guest experience and operational efficiency.}
      \resumeItemListEnd

    % Project 2: The "Mechanic/Junkyard" Project (Crucial for WDW Engineering)
    \resumeProjectHeading
      {\textbf{Automotive Restoration \& Electromechanical Repair} $|$ \emph{Hands-on Engineering}}{Miami, FL}
      \resumeItemListStart
        \resumeItem{Performed independent diagnostics and repair on passenger vehicles, troubleshooting failures in electromechanical systems including alternators, starter motors, and HVAC compressors.}
        \resumeItem{Sourced OEM components from salvage inventories (junkyards), assessing part viability and refurbishing hardware to restore vehicle functionality cost-effectively.}
        \resumeItem{Analyzed electrical schematics to trace and resolve complex fuse shorts and relay failures, applying systemic troubleshooting logic similar to facility asset sustainment.}
        \resumeItem{Conducted preventative maintenance on internal combustion engines, ensuring long-term reliability and compliance with operational safety standards.}
      \resumeItemListEnd

    % Project 3: The "CS/AI" Project (To show you meet the 'Required' Qualifications)
    \resumeProjectHeading
      {\textbf{AI-Powered Academic Advisor} $|$ \emph{Python, React, OpenAI API}}{Boston, MA}
      \resumeItemListStart
        \resumeItem{Developed a full-stack application using \textbf{Python} (Flask) and React to process natural language queries, translating complex academic data into accessible user recommendations.}
        \resumeItem{Optimized backend algorithms to handle concurrent user requests with low latency, ensuring high system availability.}
        \resumeItem{Designed a user-friendly frontend interface focused on accessibility, ensuring the tool was usable by students from non-technical backgrounds.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------LEADERSHIP & WORK EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cruz Technical Services (Freelance)}{Miami, FL}
      {Technical Consultant \& IT Specialist}{Jan 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Provided on-site technical support for non-technical clients, resolving hardware and software issues to restore system functionality.}
        \resumeItem{Translated complex technical constraints into plain language for clients, ensuring clarity and confidence in the repair process (similar to Guest Service interactions).}
        \resumeItem{Managed project timelines and budgets for small-scale IT infrastructure setups.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}